A Framework for Discrete Change

### 2008-11-17 papers/individual/individual.tex
-added paragraph in discussion
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/depmix@243 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

Analyzing the WPT data on an individual level allowed us to precisely estimate idiographic strategies and their progression during learning. Moreover, using DMMs, we can combine an individual and group level analysis, increasing reliability of the individual analyses whilst allowing for substantial individual differences. Previous analyses \cite<e.g.,>{Meeter2006} pre-defined individual strategies, based on participants' self-reports in \citet{Gluck2002}. Interestingly, \citet{Gluck2002} noted that these self-reports often did not correspond to the strategies evident in participants' responses. It is well known that people may find it difficult to verbalize the way in which they integrate multiple sources of information. As such, estimating strategies directly from participants' responses will result in more valid assessment of their response strategies, and provides a direct test of the validity of the strategy set identified by \citeauthor{Gluck2002}.
